Evaluation of probabilistic photometric redshift estimation approaches for \boldblue{ \textsc{The Rubin Observatory Legacy Survey of Space and Time} (LSST)}

### 2020-08-18 paper/main.tex
add couple acknowledgements
add data availability statement

%%% Here is where you should add your specific acknowledgments, remembering that some standard thanks will be added via the \code{desc-tex/ack/*.tex} and \code{contributions.tex} files.

This paper has undergone internal review in the LSST Dark Energy Science Collaboration.
The authors acknowledge feedback from the internal reviewers: Daniel Gruen, Markus Rau, and Michael Troxel. % REQUIRED if true

@@

The authors express immense gratitude to Alex Abate, without whom this paper would not have gotten started.
% The authors would like to thank their LSST-DESC publication review committee for comments that improved the paper draft.
% hack event acknowledgments are important
We thank Stony Brook University for hosting the Summer 2017 LSST-DESC Hack Day at which this work was partially completed.

@@

>>>>

%%% Here is where you should add your specific acknowledgments, remembering that some standard thanks will be added via the \code{desc-tex/ack/*.tex} and \code{contributions.tex} files.
The authors would like to thank the journal referee, who made many insightful suggestions that improved the draft.
This paper has undergone internal review in the LSST Dark Energy Science Collaboration.
The authors acknowledge feedback from the internal reviewers: Daniel Gruen, Markus Rau, and Michael Troxel. % REQUIRED if true

@@

The authors express immense gratitude to Alex Abate, without whom this paper would not have gotten started.  We would also like to thank Ofer Lahav and Will Hartley for contributions during the writing of the draft.
% The authors would like to thank their LSST-DESC publication review committee for comments that improved the paper draft.
% hack event acknowledgments are important
We thank Stony Brook University for hosting the Summer 2017 LSST-DESC Hack Day at which this work was partially completed.

@@

\section*{Data Availability}
The data underlying this article were provided by the makers of the Buzzard Flock simulation group by permission.  Data will be shared on request with the corresponding authors upon permission of the Buzzard Flock simulation group.  All analysis and plotting scripts used in the writing of this paper are available on GitHub in the \texttt{metric\_scripts} and \texttt{plotting\_scripts} directories of the following repository: \url{https://github.com/LSSTDESC/PZDC1paper}.
